A lottery model of density-dependent selection

### 2017-11-09 manuscript.tex

Despite this variety, fitness measures are different ways to environmentally-dependent quantify the differential reproduction and survival of individuals \citep{metcalf_2007}.

relative fitness is almost entirely divorced from population ecology.

>>>>

Despite this variety, in principle all fitness measures are ultimately ways to quantify an individual's potential for reproduction and survival \citep{metcalf_2007}. Yet the shifting-frequency relative view of fitness stands out as particularly divorced from population ecology.
